### 2020-05-21 Report/aws_325ghz_study.tex
Some polishing of Sec 6 in the report.

\thispagestyle{empty}
\noindent
\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
Satellite (AWS) high frequency channels} \vspace{8mm}\\
{\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
Department of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

\section*{Summary}
%
To written \dots

@@

\subsection{Comparison to \citet{rekha2012potential}}
%
Results from \citet{rekha2012potential} will be used as reference. They did not
suggest specific settings of their algorithm. The main consideration of the
scheme is a threshold value. We assume below 6\,K for
this value, as it used most frequently as example in
\citet{rekha2012potential}. According to their Table~3, this results in that
2.4\% of the ``cloudy'' cases are miss-classified as ``clear''. We assume that
these cases have a cloud impact of 4 to 8\,K (i.e.\ the screening is 100\%
successful for cloud impact above 8\,K). For a 6\,K threshold 41\% of the
``clear'' cases are classified as ``cloudy'' and a removed in the screening
process.

@@

A statistical comparison of the simulations to actual ATMS data, for channels
16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
Figure~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
were selected as CloudSat operates only during the day part of the orbit since
2011. For the channels around 183\,GHz, the ATMS characteristics are not fully
simulated. The ATMS channel widths are considered, but as AWS is only covering
the lower wing of the 183\,GHz transition the upper sideband of ATMS is not
included.

@@

In Figure~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences to Fig.~\ref{fig:tb:r000}  are small for 183 and
325\,GHz for the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 325\,GHz, but the influence of the surface
reflectivity is considerably lower. [* Comment somewhere on the implications of
this for retrievals at high latitudes *] Beside for the tropical case, for
229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

@@

\section{Cloud correction by a simple scheme}
%
\subsection{Formulation of correction scheme}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=65mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted against cloud impact in AWS-34. The black curve represents the line of best fit as a third order polynomial. Red and green color represent the clear and cloudy cases respectively in the simulation dataset. The blue vertical line represents the clear-sky screening threshold in the measurements for noise-index = 0.2\,K   }
	\label{fig:fit:c34-42}
\end{figure}
%
In this section, the 325\,GHz three channel option is evaluated for detection and correction of the ice-cloud cases in 183\,GHz channels. Combinations of brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used as a measure of the cloud impact.  A regression based approach is used to estimate the adjustment need to predict the clear-sky values.

Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz respectively, and Tb1 and Tb2 represent the corresponding TB. The correction scheme formulates a relationship between the cloud impact in C1 to the TB differences between C1 and C2:
\begin{equation}
Tb1_{as}-Tb2_{cs} = f(x_m)
\label{eq:TB:diff}
\end{equation}
where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.

The combinations of C1 and C2 are selected by matching their weighting functions as shown in  Figure~\ref{fig:3ch:prel}. Five  183 and 325\,GHz paired combinations are possible, for example one such paired combination is AWS-34 and AWS-42. For each of the five 183\,GHz channels, the correction scheme is derived from its corresponding counterpart in 325\,GHz channel.

As an example, the relationship between the TB differences for C1 and C2 and the cloud impact in C1 is shown in  Figure~\ref{fig:fit:c34-42}. For this particular case, C1 is AWS-34 and C2 is AWS-42, and around 125000 simulations are used. The two variables have a reasonably strong correlation for small TB differences, but as the impact of cloud increases the correlations are poor. The data can be fitted to linear or non-linear models. The fitted model can be used to interpolate the adjustment required to compensate the brightness temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which do not show any reasonable correlation, cases with $Tb2-Tb1$< -40\,K  are excluded in the fit. Also, cases with $Tb2-Tb1$ < 0.2\,K (red color dots) are assumed to be clear are not included in the model.

Before correcting the measurements, it is important to correctly classify all the cases into clear or cloudy. To avoid any undesirable adjustment of the clear cases, a clear-sky screening is added  to the correction scheme. In this screening, we assume that for clear cases, the average differences of the measurements to their noise-free clear-sky values are of the order of the instrument noise. Further in the text, we refer this value of noise as ``noise-index''. Assuming the function $f$ in eqn~\ref{eq:TB:diff} to be invertible, and if $x_{cs}$  represents the noise-index, the TB difference between the measurements from C1 and C2 for the noise-index can be used as a measure of clear-sky screening: ($dtb_{cs}$):
\begin{equation}
dtb_{cs}= f_{cs}^{-1}(x_{cs}) 
\label{eq:dtb}
\end{equation}
The value of $dtb_{cs}$ is not constant and shall depend on the the combination of 183 GHz and 325 GHz used. The measurements with TB difference between C2 and C1 less than $dtb_{cs}$ are considered cloudy and are corrected. In Figure~\ref{fig:correction:c34-42}, the blue dotted line represents the clear-sky screening cut-off when noise-index = 0.2\,K. All measurements to the left of this line are classified as cloudy, and vice-versa. For the dataset shown in the figure, around 15\% of the total cases were classified as clear. The sensitivity of noise-index is discussed in detail in the next section. 
\subsection{Application of correction scheme}
\begin{figure}[!th]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=85mm]{PDF_corrected_AWS-34_AWS-42}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction, corrected using a linear, quadratic and cubic model. The spread of noise is also shown as reference. The measurements have been corrected using brightness temperatures from AWS-42. }
	\label{fig:correction:c34-42}
\end{figure}
%

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction. The measurements have been corrected using a cubic model. The different datasets are:- thinned: 50\% of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements are filtered with noise-index = 1$\sigma$,   corrected (1$\sigma$): cloudy measurements are corrected with noise-index = 1$\sigma$, sreerekha et al: cloud filtering according to criteria described in \cite{rekha2012potential}.}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
		\hline
Noise             &   0.00 &  0.63 &              -0.01 &                - \\
uncorrected       &  -0.30 &  1.00 &              -2.64 &                - \\
filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 &             13.05 \\
corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.48 &               13.05 \\
corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.69 &                7.21 \\
sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\

		\hline
	\end{tabular}
	\caption{Various metrics for different subsets of the measurement dataset. The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
	\label{tab:correction:stats:34:42}
\end{table}
%
In this section, we test the applicability of the correction scheme in detail. To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2. Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. As an example, the results from the channel combination AWS-34 and AWS-42 are shown.

To test the efficacy of the correction scheme, three different models :linear, quadratic and cubic are evaluated to fit the TB differences between C1 and C2. For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too cloudy'' and are not corrected.  The clear-sky adjustment for all eligible measurements (without clear-sky screening) is calculated from all three models, and the three predicted datasets are compared. The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations. The occurrence frequency of the deviations from three models is shown in Figure~\ref{fig:correction:c34-42}. The occurence frequency of the all measurement without any filtering or correction is also plotted as reference (orange color). If all measurements are devoid of any cloud impact, the deviations should follow the gaussian distribution of noise. However, in real scenarios, the distribution is skewed due to the impact of clouds. It should also be noted that since no clear-sky screening was included in the measurements, the measurements with zero deviation to noise-free clear-sky were reduced. This indicates that it is extremely important to correctly classify the cases as clear/cloudy. Among the three models, the quadratic and cubic models work better than the linear model. Both quadratic and cubic models are able to correct the cloud impact in the measurements, however the values of average bias indicates that the cubic model performs better. The average deviation in the dataset is -0.82\,K and after correction with a cubic model, it reduces to -0.02\,K, while for quadratic model, the average bias after correction is 0.24\,K. For all other results described in this section, a cubic model is used.

Before applying the clear-sky screening, the measurement dataset was also thinned in order to improve the representation of the cloudy cases. Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were underrepresented than the observations. Removing 50\% of the clear-sky cases, helped in improving the percentage of total cloudy cases in the database. Further in the text, results from only thinned dataset are described.

To implement the clear-sky screening as discussed in the previous section, two different values of the noise-index are tested : $1\sigma$ and  $2\sigma$, where $\sigma$ is the standard deviation of noise. For both values of noise-index the corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42:thinned} shows the results when only the screened cloudy cases are corrected/rejected. Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats:34:42}. The results from \cite{rekha2012potential} are also shown as reference. In their approach, the cases with TB difference between AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected. Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt in other 183GHz channels is also rejected. In order to have a fair comparison of our approach with  \cite{rekha2012potential}, we also include a dataset where all the cloudy cases according to the clear-sky screening are filtered out from the measurements. The metrics from this dataset are also provided in under label ``filtered''.  For all datasets shown in the table, we assume that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''. Such cases form 5\% of the thinned dataset and are not included in the statistics.

The distribution of the deviations in the filtered data (both with approach described by sreerekha et al and the clear-sky screening) is non-Gaussian.  The right side of the distribution follows the measurement noise while the left side is skewed. The skewness in the distribution is due to cloud impacts which go undetected. These cases have cloud impact less than the threshold value and are misclassfied as clear. The frequency of such cases is higher in Sreerekha et al approach than the clear-ksy screening presented here. The measure of skewness is also smaller for the clear-sky screening. In the report by \cite{rekha2012potential} they mention that for 6\,K threshold value, around 2.4\% of the cloudy cases are misclassfied as clear. For this value of threshold, 41\% of the clear cases are also classfied as cloudy and rejected.

The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through clear-sky cutoff ($dtb_{cs}$). When the clear-sky screening is applied to this dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$ corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are classified as cloudy. These cloudy cases are corrected according to the cubic model. After correction, the average deviation to the clear-sky noise-free values in the corrected measurements should be closer to zero than uncorrected measurements. Before correction, the average bias for measurements is -0.30\,K but after correction it reduces to -0.06\,K and -0.11\,K for the two values of the noise-index respectively. This indicates that a larger value of noise-index increases the probability of falsely classifying clear cases as cloudy. 
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Figure~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

As a reference, we also apply the correction scheme described above to correct AWS-32 using AWS-4X. In this case, C1 and C2 are AWS-32 and AWS-4X. The TB correlations between AWS-32 and AWS-4X are poor and show a large spread particularly for large cloud impacts [figure not shown]. We fit the data to a cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K. Also cases with TB difference less than 0.2\,K are classified as clear and are not included in the fit. The clear-sky screening is also  evaluated for noise-index = 1$\sigma$ and $2\sigma$.
Figure~\ref{fig:correction:c32-4X:thinned} shows the deviations to clear-sky values before and after correction, and the corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}. As evident from the figure, \cite{rekha2012potential} classifies all measurements with cloud impact greater than 6\,K as cloudy, but a significant skewness in the distribution indicates misclassfication of cloudy cases. However, the frequency of misclassfied cases is significantly lower for our clear-sky screening. With \cite{rekha2012potential}'s approach, around 62\% of the measurements are rejected as cloudy, but in our approach, 84\% of the cases are classified as cloudy. This clearly indicates a high rate of misclassification of the clear cases. 
\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
		&   [K]  &   [K] & skewness[K] 		& filtered/corrected [\%]\\
		\hline
Noise             &  -0.00 &  0.45 &               0.02 &                - \\
uncorrected       &  -0.62 &  1.76 &              -4.61 &                - \\
filtered($1\sigma$)  &  -0.21 &  0.52 &              -0.65 &               84.49 \\
corrected($1\sigma$) &   0.88 &  1.76 &              -1.29 &               84.49 \\
corrected($2\sigma$) &   0.76 &  1.80 &              -1.06 &               68.00 \\
sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
The correction scheme can also be extended to other combinations of 183GHz and 325GHz. The other possible combinations for clear-sky screening are: AWS-32 and AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.
% 
Table~\ref{tab:correction:stats:32:41}  shows the statistics when AWS-32 is corrected using AWS-41. The statistics of the filtered dataset are better than the approach by \cite{rekha2012potential}. However, a very high rejection fraction (85\%) indicates that a large percentage of clear cases are misclassfied as cloudy.

@@

@@

\section{Conclusion}
%
\dots

>>>>

\thispagestyle{empty}
\noindent
\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
Satellite (AWS) high frequency channels} \vspace{8mm}\\
{\bf Patrick Eriksson, Inderpreet Kaur and Simon Pfreundschuh}\\
Department of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden\vspace{10mm}

\section*{Summary}
%
To be written \dots

@@

\subsection{Comparison to \citet{rekha2012potential}}
\label{sec:rekha}
%
Results from \citet{rekha2012potential} will be used as reference. They did not
suggest specific settings of their algorithm. The main consideration of the
scheme is a threshold value. We assume below 6\,K for
this value, as it used most frequently as example in
\citet{rekha2012potential}. According to their Table~3, this results in that
2.4\% of the ``cloudy'' cases are miss-classified as ``clear''. We assume that
these cases have a cloud impact of 4 to 8\,K (i.e.\ the screening is 100\%
successful for cloud impact above 8\,K). For a 6\,K threshold 41\% of the
``clear'' cases are classified as ``cloudy'' and a removed in the screening
process.

@@

A statistical comparison of the simulations to actual ATMS data, for channels
16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
Fig.~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
were selected as CloudSat operates only during the day part of the orbit since
2011. For the channels around 183\,GHz, the ATMS characteristics are not fully
simulated. The ATMS channel widths are considered, but as AWS is only covering
the lower wing of the 183\,GHz transition the upper sideband of ATMS is not
included.

@@

In Fig.~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences to Fig.~\ref{fig:tb:r000}  are small for 183 and
325\,GHz for the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 325\,GHz, but the influence of the surface
reflectivity is considerably lower. [* Comment somewhere on the implications of
this for retrievals at high latitudes *] Beside for the tropical case, for
229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

@@

\section{Cloud correction by a simple scheme}
%
In this section, the 325\,GHz three channel option is evaluated for detection
and correction of cloud interference in 183\,GHz channels. Combinations of
brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used
as a measure of the cloud impact. A regression based approach is used to
estimate the adjustment needed to predict the clear-sky values.

\subsection{Formulation of correction scheme}
%
Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz
respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
scheme formulates a relationship between the cloud impact in C1 to the TB
differences between C1 and C2:
\begin{equation}
Tb1_{as}-Tb2_{cs} = f(x_m)
\label{eq:TB:diff}
\end{equation}
where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.

The combinations of C1 and C2 are selected by matching their weighting
functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183 and 325\,GHz paired
combinations are possible, for example one such paired combination is AWS-34
and AWS-42. For each of the five 183\,GHz channels, the correction scheme is
derived from its corresponding counterpart in 325\,GHz channel.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. The black curve represents the line of
      best fit as a third order polynomial. Red and green color represent the
      clear and cloudy cases respectively in the simulation dataset. The blue
      vertical line represents a clear-sky screening threshold of 0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

As an example, the relationship between the TB differences for C1 and C2 and
the cloud impact in C1 is shown in Fig.~\ref{fig:fit:c34-42}. For this
particular case, C1 is AWS-34 and C2 is AWS-42, and around 125\,000 simulations
are used. The two variables have a reasonably strong correlation for small TB
differences, but as the impact of cloud increases the correlations gets poorer.
The data can be fitted to linear or non-linear models. The fitted model can be
used to interpolate the adjustment required to compensate the brightness
temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
assumed to be clear-sky are not included in the model.

It is also important to have a manner for making a clear/cloudy classification.
This is useful for making a filtering in line with \citep{rekha2012potential},
but is also needed in the correction scheme. The later is the case as the
polynomial fit derived gives a non-zero correction for clear-sky cases. In
Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
and C2 (red dots) have a mean close to zero (as the weighting functions are
well matched), but this is not the case for all channel combinations and some
general rule for finding a threshold value (with respect to $x_m$) must be
formulated. The polynomial fit will be used also for this part.

%Before correcting the measurements, it is important to correctly classify all
%the cases into clear or cloudy. To avoid any undesirable adjustment of the
%clear cases, a clear-sky screening is added  to the correction scheme. In this
%screening, we assume that for clear cases, the average differences of the
%measurements to their noise-free clear-sky values are of the order of the
%instrument noise. Further in the text, we refer this value of noise as
%``noise-index''.
%Assuming the function $f$ in eqn~\ref{eq:TB:diff} to be invertible, and if $x_{cs}$  represents the noise-index, the TB difference between the measurements from C1 and C2 for the noise-index can be used as a measure of clear-sky screening: ($dtb_{cs}$):

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
dtb_{cs}= f_{cs}^{-1}(x_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitide of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).

%The value of $dtb_{cs}$ is not constant and shall depend on the the combination
%of 183 GHz and 325 GHz used. The measurements with TB difference between C2 and
%C1 less than $dtb_{cs}$ are considered cloudy and are corrected. In
%Fig.~\ref{fig:correction:c34-42}, the blue dotted line represents the clear-sky
%screening cut-off when noise-index = 0.2\,K. All measurements to the left of
%this line are classified as cloudy, and vice-versa. For the dataset shown in
%the figure, around 15\% of the total cases were classified as clear. The
%sensitivity of noise-index is discussed in detail in the next section.

\subsection{Application of correction scheme}
\begin{figure}[!p]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=90mm]{PDF_corrected_AWS-34_AWS-42}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The spread of noise is also shown as
      reference. The measurements have been corrected using brightness
      temperatures from AWS-42. }
	\label{fig:correction:c34-42}
\end{figure}
%

\begin{figure}[!]
	\centering
	\includegraphics[height=90mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: thinned: 50\%
      of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements
      are filtered with noise-index = 1$\sigma$, corrected (1$\sigma$): cloudy
      measurements are corrected with noise-index = 1$\sigma$, Sreerekha et al:
      cloud filtering according to criteria described in
      \cite{rekha2012potential}.}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
		\hline
Noise             &   0.00 &  0.63 &              -0.01 &                - \\
uncorrected       &  -0.30 &  1.00 &              -2.64 &                - \\
filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 &             13.05 \\
corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.48 &               13.05 \\
corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.69 &                7.21 \\
Sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\

		\hline
	\end{tabular}
	\caption{Various metrics for different subsets of the measurement dataset. The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
	\label{tab:correction:stats:34:42}
\end{table}
%
In this section, we test the applicability of the correction scheme in detail. To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2. Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. As an example, the results from the channel combination AWS-34 and AWS-42 are shown.

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. The clear-sky adjustment for all eligible
measurements (without clear-sky screening) is calculated from all three models,
and the three predicted datasets are compared. The error in the predicted
measurements is assessed by calculating the deviation to noise-free clear-sky
observations. The occurrence frequency of the deviations from three models is
shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the all
measurement without any filtering or correction is also plotted as reference
(orange color). If all measurements are devoid of any cloud impact, the
deviations should follow the gaussian distribution of noise. However, in real
scenarios, the distribution is skewed due to the impact of clouds. It should
also be noted that since no clear-sky screening was included in the
measurements, the measurements with zero deviation to noise-free clear-sky were
reduced. This indicates that it is extremely important to correctly classify
the cases as clear/cloudy. Among the three models, the quadratic and cubic
models work better than the linear model. Both quadratic and cubic models are
able to correct the cloud impact in the measurements, however the values of
average bias indicates that the cubic model performs better. The average
deviation in the dataset is -0.82\,K and after correction with a cubic model,
it reduces to -0.02\,K, while for quadratic model, the average bias after
correction is 0.24\,K. For all other results described in this section, a cubic
model is used.

Before applying the clear-sky screening, the measurement dataset was also
thinned in order to improve the representation of the cloudy cases. Validation
of the simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the
cloudy cases were underrepresented than the observations. Removing 50\% of the
clear-sky cases, helped in improving the percentage of total cloudy cases in
the database. Further in the text, results from only thinned dataset are
described.

To implement the clear-sky screening as discussed in the previous section, two
different values of the noise-index are tested: $1\sigma$ and $2\sigma$, where
$\sigma$ is the standard deviation of noise. For both values of noise-index the
corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using
Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42:thinned} shows the results
when only the screened cloudy cases are corrected/rejected. Various metrics
from the corrected measurements are also shown in
Table~\ref{tab:correction:stats:34:42}. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In their approach, the cases with TB difference between
AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt
in other 183GHz channels is also rejected. In order to have a fair comparison
of our approach with \cite{rekha2012potential}, we also include a dataset where
all the cloudy cases according to the clear-sky screening are filtered out from
the measurements. The metrics from this dataset are also provided in under
label ``filtered''. For all datasets shown in the table, we assume that cases
with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''.
%Such cases form 5\% of the thinned
%dataset and are not included in the statistics.

The distribution of the deviations in the filtered data (both with approach
described by Sreerekha et al and the clear-sky screening) is non-Gaussian. The
right side of the distribution follows the measurement noise while the left
side is skewed. The skewness in the distribution is due to cloud impacts which
go undetected. These cases have cloud impact less than the threshold value and
are misclassfied as clear. The frequency of such cases is higher in Sreerekha
et al approach than the clear-ksy screening presented here. The measure of
skewness is also smaller for the clear-sky screening. 
%In the report by
%\cite{rekha2012potential} they mention that for 6\,K threshold value, around
%2.4\% of the cloudy cases are misclassfied as clear. For this value of
%threshold, 41\% of the clear cases are also classfied as cloudy and rejected.

The regression approach described here does not provide any way to correct the
misclassfied cases, but the frequency of such cases can be controlled through
clear-sky cutoff ($dtb_{cs}$). When the clear-sky screening is applied to this
dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$
corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are
classified as cloudy. These cloudy cases are corrected according to the cubic
model. After correction, the average deviation to the clear-sky noise-free
values in the corrected measurements should be closer to zero than uncorrected
measurements. Before correction, the average bias for measurements is -0.30\,K
but after correction it reduces to -0.06\,K and -0.11\,K for the two values of
the noise-index respectively. This indicates that a larger value of noise-index
increases the probability of falsely classifying clear cases as cloudy.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

As a reference with respect to having a channel at 229\,GHz, we also apply the
correction scheme described above to correct AWS-32 using AWS-4X (following
\citet{rekha2012potential}). In this case, C1 and C2 are AWS-32 and AWS-4X. The
TB correlations between AWS-32 and AWS-4X are poor and show a large spread
particularly for large cloud impacts (not shown). We fit the data to a
cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K. Also cases with TB
difference less than 0.2\,K are classified as clear and are not included in the
fit. The clear-sky screening is also evaluated for noise-index = 1$\sigma$ and
$2\sigma$. Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations to
clear-sky values before and after correction, and the corresponding metrics are
provided in Table~\ref{tab:correction:stats:32:4X}. As evident from the figure,
\cite{rekha2012potential} classifies all measurements with cloud impact greater
than 6\,K as cloudy, but a significant skewness in the distribution indicates
misclassfication of cloudy cases. However, the frequency of misclassfied cases
is significantly lower for our clear-sky screening. With
\cite{rekha2012potential}'s approach, around 62\% of the measurements are
rejected as cloudy, but in our approach, 84\% of the cases are classified as
cloudy. This clearly indicates a high rate of misclassification of the clear
cases.
\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
		&   [K]  &   [K] & skewness[K] 		& filtered/corrected [\%]\\
		\hline
Noise             &  -0.00 &  0.45 &               0.02 &                - \\
uncorrected       &  -0.62 &  1.76 &              -4.61 &                - \\
filtered($1\sigma$)  &  -0.21 &  0.52 &              -0.65 &               84.49 \\
corrected($1\sigma$) &   0.88 &  1.76 &              -1.29 &               84.49 \\
corrected($2\sigma$) &   0.76 &  1.80 &              -1.06 &               68.00 \\
Sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
The correction scheme can also be extended to other combinations of 183GHz and
325GHz. The most relevant combinations for clear-sky screening are: AWS-32 and
AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The statistics of the filtered dataset are better than
the approach by \cite{rekha2012potential}, while the corrected data have poorer
statistics. This is not surprising as the weighting function match between 
AWS-32 and  AWS-41 is poor.
%However, a very high rejection
%fraction (85\%) indicates that a large percentage of clear cases are
%misclassfied as cloudy.

@@

(Just a start, to not forget these points)

@@

\section{Conclusion}
%
This study compares the options of having a channel at 229\,GHz or having some
around 325\,GHz from a single perspective, cloud filtering(corection of
183\,GHz data. There could be other important reasons to consider for the
selection.

\dots
